Supplementary methods

### 2021-06-28 text/supplemental_methods.Rmd
Update sm3 fig with effage tis and cl

```{r sm3, fig.height=3, fig.width=3}
ggplot(data.frame(x=0:30),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,1.2,.2),geom="area", aes(fill = "ktis"))+ 
  stat_function(fun=function(x) dgamma(x,3.5,2.5),geom="area", aes(fill = "kcl"))+ 
  labs(title=expression(paste("Prior for k"["tis"], "and k"["cl"])),x= "k value", y = "Probability Density") +
  theme_classic() + scale_x_continuous(limits = c(0, 20), breaks = c(seq(0,20, by =5))) +
  scale_y_continuous(limits = c(0,0.75), breaks = c(seq(0,0.75, by = 0.25))) +
  scale_fill_manual(values = c(alpha("#E69F00", 0.5),alpha("#0072B2", 0.5)),
                    labels = c(expression(paste("k"["cl"])), expression(paste("k"["tis"])))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line(),
        legend.position = c(0.8, 0.8),
        legend.spacing.y = unit(0, "mm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.size = unit(0.75,"line"),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))
```

**Fig SM3. Priors for the tissue and class coefficients.** The tissue
coefficient is chosen to admit ages between 40 and 100 years old as a baseline
age. Within a given tissue, the class parameter multiplies the tissue value and
is given a peak density at 1, and a credible range from near 0.6 to 1.4,
reflecting our expectation of a moderate multiplicative perturbation of
variation across the classes.

>>>>

```{r sm3, fig.height=3, fig.width=3}
sm3.1 <- ggplot(data.frame(x=0:110),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,30.0,29.0/65),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(30, 110), breaks = c(seq(30,110, by =10))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for Effage"["tis"])), y = "Probability Density")

sm3.2 <- ggplot(data.frame(x=0:3),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,50.0,49.0/1.0),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 1.6), breaks = c(seq(0.6, 1.5, by = 0.2))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for Effage"["cl"])), y = "Probability Density")

layout = "
AABB
AABB
"

sm3.1 + sm3.2 + plot_annotation(tag_levels = "A") + plot_layout(design = layout)
```

**Fig SM3. Priors for the tissue and class coefficients.** A) The tissue
coefficient is chosen to admit ages between 40 and 100 years old as a baseline
age. B) Within a given tissue, the class parameter multiplies the tissue value and
is given a peak density at 1, and a credible range from near 0.6 to 1.4,
reflecting our expectation of a moderate multiplicative perturbation of
variation across the classes.
